Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Modified according to Matheus's comments/added boxplots/aded future work and conclusion.

Code cloning is an activity of reusing source code by copying and pasting. It normally occurs in software development and account from 7\% to 23\% in typical software systems~\cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others suggest that in some cases clones are not harmful or even beneficial~\cite{Saini2016,Kapser2006}.

Code cloning can also have side effects of violating software licenses and software vulnerabilities. Carelessly cloning code from one project to another project with a different license may cause a software licensing violation~\cite{German2009}. This also happens within the context of online Q\&A websites such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow potentially violate software licenses. Security is also among the main concerns when code is copied from online source. Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, offers less secure code than books or the official Android documentation~\cite{Acar2016}. Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement {\small{\texttt{RawComparator}}} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how {\small{\texttt{hadoop}}} implements the {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class. The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class but it is extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}. We can obviously see that they are highly similar except one line, {\small{\verb|buffer.reset(null,0,0);|}}, is added in the latest version after {\small{\verb|key2.readFields(buffer);|}}. The added line is intended for cleaning up the reference in the {\small{\verb|buffer|}} variable. While this change has already been introduced into the {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and their originals. %The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 315,786,118 similar code snippet pairs and manually investigated 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses. In addition, 64 out of the 112 online code clones on Stack Overflow are outdated and questionable for being reused.

@@

\section{Empirical Study}
We performed an empirical study of online code clones between Stack Overflow and 111 Java open source projects to answer the following research questions: \\ 
\textbf{RQ1 (online code clones):} \textit{To what extent  is source code cloned between Stack Overflow and open source projects?} We quantitatively measured the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem. \newline
\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorised online clones into seven categories according to our online code cloning pattern scheme. This gave us more insights to why online code clones are created.
\newline
\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them. \newline
\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software reusing them.

@@

\subsection{Experimental Framework}
To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}. We processed two datasets, 144,075 code snippets from Java accept answers on Stack Overflow and 111 open source projects from Qualitas corpus. Java code snippets were extracted from Stack Overflow posts. We prepared the Java code in both datasets by removing comments and pretty-printing to increase the accuracy of clone detection. Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times. Each run was composed of the whole Stack Overflow data and a single Qualitas project. We repeated the process until we covered 111 projects.

We then converted the clone reports to the General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file. GCF provides a common format for clones which enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted, if needed, without any changes in the analysis. Simian did not provide an option to detect clones between two locations. Hence the Simian GCF clone report was pruned to contain only clone pairs between Stack Overflow and Qualitas projects. In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed. NiCad provides an option to detect clones from two locations so no pruning is needed. We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates. However, the large amount of generated clone pairs hindered us from looking at all of them. Random sampling of clones could be done but may return mostly non-meaningful clones. Instead, we selected clone pair candidates by relying on agreement of clone detectors. If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair. To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step generated \textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since they obtained agreement from both tools. Then, pairs reported by Simian and NiCad that did not find agreement were rejected as \textbf{disagreed clone pairs}. The disagreed clone pairs were clones with less confidence than the agreed ones. Finally, agreed and disagreed clone pairs have been looked at manually by two of the authors.

In the manual inspection process, we classified clones into seven categories according to information observed from code comments and natural text in the Stack Overflow answer. This process took approximately a month until we successfully investigated 3,632 clone pairs. Clone pairs that were classified as false clones, boiler-plate code, or IDE-generated are not very interesting and were ignore in the analysis of outdated code and licensing violation. 
We compared the licensing information of 668 remaining clone pairs for possibilities of software licensing violations. Moreover, we looked at the history starting at the date of the answers to today from its git repository. With this method, we discovered \textbf{outdated code}, code that changes are made to them after it had been copied to Stack Overflow. %hence resulting in outdated clones on Stack Overflow.

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming languages to visualisation~\cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study. This resulted in a total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

@@

\subsubsection{Prioritise Clone Candidates Using Agreement}
The number of clones detected in large-scale datasets can be huge. In our study, there are in total 266,837,480 clone pairs reported. It is infeasible for humans to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confident and ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.

@@

We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1, we computed statistics on clones discovered by the tools. To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning. The patterns were derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set. For RQ3, we looked at the true positive clone pairs and checked if they are still up-to-date. Similarly, for RQ4, we also looked at the license of each clone and checked for a possibility of licensing violation.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
	\label{tab:raw_stats}
	\small
%	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
%	}
\end{table}

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported for $S_D$ and 1,531 for $S_E$ respectively. $N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a much larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs, 63,635,844 and 251,449,849 respectively. This large number of clones is expected since EvaClone configurations prefer recall~\cite{Wang2013}. $S_D$ and $N_D$ have the average clone pairs per snippet of 62 and 455 respectively. On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average. The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in a way that they report smaller clones. The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. A quick manual check of Simian's clone report revealed that there were 11 problematic snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

As displayed in \Cref{t_agreed_good_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729. %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. 
We explain them in more details below.

@@

Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria and selected for manual classification. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors. $N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

%\subsubsection{Outdated Clones}
Outdated code occurs when a piece of code has been copied from its origin to another location and later the original has been updated~\cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}. However, for online code clones, the clones are pervasive and more difficult to detect than software projects due to its large search space and a mix of natural and programming languages combined in the same post. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.

>>>>

Code cloning is an activity of reusing source code by copying and pasting. It normally occurs in software development and account from 7\% to 23\% of source code in typical software systems~\cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others suggest that in some cases clones are not harmful or even beneficial~\cite{Saini2016,Kapser2006}.

Code cloning can also have side effects such as violating software licenses and software vulnerabilities. Carelessly cloning code from one project to another project with a different license may cause a software licensing violation~\cite{German2009}. This also happens within the context of online Q\&A websites such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow potentially violate software licenses. Security is also among the main concerns when code is copied from an online source. Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, offers less secure code than books or the official Android documentation~\cite{Acar2016}.

\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement {\small{\texttt{RawComparator}}} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how {\small{\texttt{hadoop}}} implements the {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class. The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class, but at this time extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}. We can obviously see that they are highly similar except a line containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in the latest version after {\small{\verb|key2.readFields(buffer);|}}. The added line is intended for cleaning up the reference in the {\small{\verb|buffer|}} variable. While this change has already been introduced into the {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and their originals leading the users of Stack Overflow to reuse outdated code. %The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

While research has mostly focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 315,786,118 similar code snippet pairs followed by a manual classification of 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus~\cite{QualitasCorpus}.

\vspace{0.5ex}%
\noindent\textbf{2.~Investigating the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses. In addition, 64 out of the 112 online code clones from Qualitas to Stack Overflow are outdated and questionable for being reused.

@@

\section{Empirical Study}
We performed an empirical study of online code clones between Stack Overflow and 111 Java open source projects to answer the following research questions: \\ 
\textbf{RQ1 (online code clones):} \textit{To what extent  is source code cloned between Stack Overflow and open source projects?} We quantitatively measured the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem. \newline
\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorised online clones into seven categories according to our online code cloning pattern scheme. This gave us more insights to why online code clones are created.
\newline
\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the outdated Stack Overflow code examples since millions of users are potentially reusing them. \newline
\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software reusing them.

@@

\subsection{Experimental Framework}
To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}. We processed two datasets, 144,075 code snippets from Java accept answers on Stack Overflow and 111 open source projects from Qualitas corpus. Java code snippets were extracted from Stack Overflow posts. We prepared the Java code in both datasets by removing comments and pretty-printing to increase the accuracy of clone detection. Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to the scalability of Simian and NiCad, we partitioned the input and run the tools multiple times. Each run was composed of the whole Stack Overflow data and a single Qualitas project. We repeated the process until we covered 111 projects.

%enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted
We then converted the clone reports to the General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file. GCF provides a common format for clones which enables other clone detectors to be adopted,
if needed, without any changes in the analysis. Simian did not provide an option to detect cross-project clones between two locations. Hence the Simian GCF clone report was pruned to contain only clone pairs between Stack Overflow and Qualitas projects. In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed. NiCad provides an option to detect clones from two locations so no pruning is needed. We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates. However, the large amount of generated clone pairs hindered us from looking at all of them. Random sampling of clones could be employed. However, the risk of returning non-meaningful clones is increased. Instead, we selected clone pair candidates by relying on agreement of clone detectors. If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair. To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step generated \textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since they obtained agreement from both tools. Then, pairs reported by Simian and NiCad that did not find agreement were categorised as \textbf{disagreed clone pairs}. The disagreed clone pairs were clones with less confidence than the agreed ones. Finally, agreed and disagreed clone pairs have been looked at manually by two of the authors.

In the manual inspection process, we classified clones into seven categories according to information observed from code comments and natural text in the Stack Overflow answer. This process took approximately a month until we successfully investigated 3,632 clone pairs. Clone pairs that were classified as false clones, boiler-plate code, or IDE-generated are not very interesting and were ignore in the analysis of outdated code and licensing violation. 
We compared the licensing information of 668 remaining clone pairs for possibilities of software licensing violations. Moreover, we looked at the history starting at the date of the answers to today from its git repository. With this method, we discovered \textbf{outdated code}, i.e.~code that changes were made to them after they had been copied to Stack Overflow. %hence resulting in outdated clones on Stack Overflow.

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

\textbf{Open source systems}: we selected the established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming languages to visualisation~\cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study. This resulted in a total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

@@

\subsubsection{Prioritise Clone Candidates Using Agreement}
The number of clones detected in large-scale datasets can be huge. In our study, there are in total 266,837,480 clone pairs reported. It is infeasible for humans to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking mostly at the false clones. Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs reported by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the original definitions of \textit{good}- and \textit{ok}-match introduced in Bellon's paper~\cite{Bellon2007}.

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confidence and are ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.

@@

We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1, we computed statistics on clones discovered by the tools. To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning. The patterns were derived from Kapser et al.~\cite{Kapser2003} and augmented by common patterns found in our data set. For RQ3, we looked at the true positive clone pairs and checked if they are still up-to-date. Similarly, for RQ4, we also looked at the license of each clone and checked for a possibility of licensing violation.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
	\label{tab:raw_stats}
	\small
%	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
%			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
%	}
\end{table}

The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}. Simian with the default configuration ($S_D$) report clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets. Simian with the EvaClone configuration ($S_E$) report 1,531 snippets containing clones. NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets. NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations. In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report a larger clone pair amount of 63,635,844 and 251,449,849 pairs respectively. This is expected since EvaClone configurations prefer recall~\cite{Wang2013}. 
%Using $S_D$, we found 62 clones in average originating from a single Stack Overflow snippet. 62 and 455 respectively. On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average. 
The average clone size reported by $S_D$ is 7.72 lines which is bigger than $S_E$ (4.79 lines). Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 lines reported by $N_E$. We can see from the statistics that EvaClone tunes the tools to report smaller clones. The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. A quick manual check of Simian's clone report revealed that there were 11 problematic snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

As displayed in \Cref{t_agreed_good_clone_pairs}, after we applied clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729. %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. 
We explain them in more details below.

@@

Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors. $N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified the issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

%\subsubsection{Outdated Clones}
Outdated code occurs when a piece of code has been copied from its origin to another location and later the original has been updated~\cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}. However, for online code clones, the clones are pervasive and more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.
